---
title: "Primary Production model output"
output: flexdashboard::flex_dashboard
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "04_analysis", output_file = paste0("PP_BIO_8day_2018185_alphab-pmb-variable_uniform-profile_", format(Sys.Date(), "%Y%m%d"))) })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE)
```


```{r prelim, warning=FALSE, message=FALSE, echo=FALSE}
library(raster)
library(gridExtra)
library(oceancolouR)

# input filename (.rda extension, NOT .nc, not including path)
filename <- "BIO_NWA_8day_2018185_alphab-pmb-variable_uniform-profile_47-55N_-53--43W.rda"

# variables to print below
method <- "BIO"
year <- 2018
month <- 7
week <- 1
doy <- 185
interval <- "8day"            # 8day or monthly
uniform_profile <- TRUE       # chla profile
gauss <- TRUE                 # if nonuniform chla profile, was the file processed using a shifted gaussian chla profile?
use_constant_alphab <- FALSE  # same alphaB value used for every pixel?
use_constant_pmb <- FALSE     # same pmb value used for every pixel?
alphab_method <- "predefined" # if same alphab used for all pixels, was it predefined (=1), or the mean or median of the region?
pmb_method <- "predefined"    # if same pmb used for all pixels, was it predefined (=1.69), or the mean or median of the region?
lat_bounds <- c(47,55)
lon_bounds <- c(-53,-43)

# variables to plot (excluding PP, which is plotted automatically)
input_variables <- list("Bathymetry"="bathy", "Chlorophyll-a"="chl", "SST"="sst", "PAR"="par", "Cloud fraction"="tcc")
LUT_variables <- list("alphaB"="alphab", "PmB"="pmb")
calculated_variables <- list("PAR"="PAR_BIO", "Spectral irradiance"="XX_BIO", "Euphotic depth"="EuphoD_BIO", "Yellow substances"="yelsub_BIO")

load(file.path("03_PP_output", interval, filename))

```

# Details

|                       |     |
|-----------------------|-----|
| **Model**             | `r method`  |
| **Year**              | `r year`  |
| **Month**             | `r month`  |
| **Month week**        | `r week`  |
| **Day of year**       | `r doy`  |
| **Composite**         | `r interval`  |
| **Latitude bounds**   | `r paste0(lat_bounds[1], " to ", lat_bounds[2], " N")`  |
| **Longitude bounds**  | `r paste0(lon_bounds[1], " to ", lon_bounds[2], " W")`  |
| **Chla profile**      | `r ifelse(uniform_profile, "uniform", ifelse(gauss, "Gaussian", "Interpolated"))`  |
| **AlphaB**            | `r ifelse(use_constant_alphab, alphab_method, "variable")`  |
| **PmB**               | `r ifelse(use_constant_pmb, pmb_method, "variable")`  |


<br>

**PI curve parameters**:  
For *alphaB* (initial slope of the PI curve) and *PmB* (maximum photosynthetic rate), "variable" means that the value varies from pixel to pixel based on a look-up table. "Predefined" means *alphaB*=1 and *PmB*=1.69 (the same values used in the Laval model) for every pixel. "Mean" or "median" indicates that the same value is used for every pixel, calculated as the mean/median of the *alphaB* or *PmB* values from the look-up table (within the selected latitude/longitude boundaries of the image).  

**Intermediate variables**:  
*PAR*, *Spectral irradiance*, and *Yellow substances* have been integrated over depth and time, and *Euphotic depth* has been integrated over time.  



# Rasters

Column {data-width=400}
-------------------------------------

### Input variables

```{r, fig.width=3, fig.height=10}
rast_list <- list()
for (i in 1:length(input_variables)) {
    tmp_rast <- var_to_rast(df = data.frame(bin=rda_output$bin, var=rda_output[,input_variables[[i]]], stringsAsFactors = FALSE),
                            ext = c(lon_bounds, lat_bounds))
    rast_list[[names(input_variables)[i]]] <- spplot(tmp_rast,
                                                     ylab=names(input_variables)[i],
                                                     par.settings=list(layout.heights=list(top.padding=0, axis.xlab.padding=0, key.sub.padding=0, bottom.padding=0)))
}
grid.arrange(grobs=rast_list, nrow=length(input_variables), heights=rep(1,length(input_variables)))
```


Column {data-width=400}
-------------------------------------

### PI curve parameters (look-up table)

```{r, fig.width=5, fig.height=3}
rast_list <- list()
for (i in 1:length(LUT_variables)) {
    tmp_rast <- var_to_rast(df = data.frame(bin=rda_output$bin, var=rda_output[,LUT_variables[[i]]], stringsAsFactors = FALSE),
                            ext = c(lon_bounds, lat_bounds))
    rast_list[[names(LUT_variables)[i]]] <- spplot(tmp_rast,
                                                   main=names(LUT_variables)[i],
                                                   par.settings=list(layout.heights=list(top.padding=0, axis.xlab.padding=0, key.sub.padding=0, bottom.padding=0)))
}
grid.arrange(grobs=rast_list, ncol=length(LUT_variables), widths=c(11,10))
```


### Primary production

```{r, fig.width=4, fig.height=4}
tmp_rast <- var_to_rast(df = data.frame(bin=rda_output$bin, var=rda_output$PP_BIO, stringsAsFactors = FALSE),
                        ext = c(lon_bounds, lat_bounds))
spplot(tmp_rast, main="Primary production", par.settings=list(layout.heights=list(top.padding=0, axis.xlab.padding=0, key.sub.padding=0, bottom.padding=0)))
```


Column {data-width=400}
-------------------------------------

### Intermediate variables

```{r, fig.width=3, fig.height=9}
rast_list <- list()
for (i in 1:length(calculated_variables)) {
    tmp_rast <- var_to_rast(df = data.frame(bin=rda_output$bin, var=rda_output[,calculated_variables[[i]]], stringsAsFactors = FALSE),
                            ext = c(lon_bounds, lat_bounds))
    rast_list[[names(calculated_variables)[i]]] <- spplot(tmp_rast,
                                                          ylab=names(calculated_variables)[i],
                                                          par.settings=list(layout.heights=list(top.padding=0, axis.xlab.padding=0, key.sub.padding=0, bottom.padding=0)))
}
grid.arrange(grobs=rast_list, nrow=length(calculated_variables), heights=rep(1, length(calculated_variables)))
```


