---
title: "Primary Production model comparisons"
output: flexdashboard::flex_dashboard
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "04_analysis", output_file = paste0("PP_BIO-VGPM_comparison_8day_2018185_alphab-variable-pmb-constant_uniform-profile_", format(Sys.Date(), "%Y%m%d"))) })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE)
```


```{r prelim, echo=FALSE, warning=FALSE, message=FALSE}
library(raster)
library(ggplot2)
library(gridExtra)
library(oceancolouR)
library(ncdf4)
library(stringr)

vgpm_file <- "PP_VGPM/8day_2160x4320/vgpm.2012185.hdf"
bio_file <- "03_PP_output/8day/BIO_NWA_8day_2018185_alphab-pmb-variable_uniform-profile_47-55N_-53--43W.nc"


# variables to print below
method <- "BIO"
year <- 2018
month <- 7
week <- 1
doy <- 185
interval <- "8day"            # 8day or monthly
uniform_profile <- TRUE       # chla profile
gauss <- TRUE                 # if nonuniform chla profile, was the file processed using a shifted gaussian chla profile?
use_constant_alphab <- FALSE  # same alphaB value used for every pixel?
use_constant_pmb <- FALSE     # same pmb value used for every pixel?
alphab_method <- "predefined" # if same alphab used for all pixels, was it predefined (=1), or the mean or median of the region?
pmb_method <- "predefined"    # if same pmb used for all pixels, was it predefined (=1.69), or the mean or median of the region?
lat_bounds <- c(47,55)
lon_bounds <- c(-53,-43)
```


# Details

This is a comparison of the BIO primary production model to Standard VGPM from VIIRS data, using uniform biomass profiles.  

8day VGPM PP images: http://orca.science.oregonstate.edu/2160.by.4320.8day.hdf.vgpm.v.chl.v.sst.php  

Color scales: mean +- 2 standard deviations  

% Difference = 100 * (BIO - VGPM) / VGPM  

Possible sources of discrepancies between the two, aside from the model:  

  - BIO uses different alphaB / PmB for each pixel, based on a look-up table that takes year/day and satellite CHL and SST as input and uses nearest statistical distance and yaImpute package to get the closest in situ CHL/SST and their corresponding PI curve parameters  
  - Different CHL / SST / PAR / TCC input?  
  - BIO does not fill gaps  


### BIO model/image details:  

|                       |     |
|-----------------------|-----|
| **Year**              | `r year`  |
| **Month**             | `r month`  |
| **Month week**        | `r week`  |
| **Day of year**       | `r doy`  |
| **Composite**         | `r interval`  |
| **Latitude bounds**   | `r paste0(lat_bounds[1], " to ", lat_bounds[2], " N")`  |
| **Longitude bounds**  | `r paste0(lon_bounds[1], " to ", lon_bounds[2], " W")`  |
| **Chla profile**      | `r ifelse(uniform_profile, "uniform", ifelse(gauss, "Gaussian", "Interpolated"))`  |
| **AlphaB**            | `r ifelse(use_constant_alphab, alphab_method, "variable")`  |
| **PmB**               | `r ifelse(use_constant_pmb, pmb_method, "variable")`  |


### VGPM model details (from their website):  
    
http://sites.science.oregonstate.edu/ocean.productivity/vgpm.model.php  
--> "MODEL DESCRIPTIONS"  
--> "VGPM"  


# Rasters

```{r plots, echo=FALSE, results='asis', fig.align='center', fig.width=10}

vgpm_rast <- raster(vgpm_file)

data("nwa_bins_4km")
bio_nc <- nc_open(bio_file)
bio_pp <- ncvar_get(bio_nc, "PP")
nc_close(bio_nc)
bio_rast <- var_to_rast(df=data.frame(bin=nwa_bins_4km, pp=bio_pp), ext=c(lon_bounds, lat_bounds))

crs(vgpm_rast) <- crs(bio_rast)
extent(vgpm_rast) <- extent(c(xmin=-180,xmax=180,ymin=-90,ymax=90))

vgpm_rast <- crop(vgpm_rast, extent(bio_rast))
vgpm_rast[vgpm_rast < 0] <- NA

# https://www.neonscience.org/dc-raster-calculations-r
# For raster math, make sure the rasters have the same CRS, resolution, and defined minimum and maximum values
vgpm_rast <- resample(vgpm_rast, bio_rast)

names(vgpm_rast) <- "VGPM"
names(bio_rast) <- toupper(method)

# Adjust the range of the color scale to +- 2 standard deviations
vgpm_vec <- as.numeric(as.vector(vgpm_rast))
bio_vec <- as.numeric(as.vector(bio_rast))
full_vec <- c(vgpm_vec,bio_vec)
full_range <- c(mean(full_vec,na.rm=T) - 2*sd(full_vec,na.rm=T),
                mean(full_vec,na.rm=T) + 2*sd(full_vec,na.rm=T))

# Make a raster of the difference between them, on a separate color scale
diff_rast <- ((bio_rast - vgpm_rast)/vgpm_rast) * 100
names(diff_rast) <- "% Difference"
diff_vec <- as.numeric(as.vector(diff_rast))
diff_range <- c(mean(diff_vec,na.rm=T) - 2*sd(diff_vec,na.rm=T),
                mean(diff_vec,na.rm=T) + 2*sd(diff_vec,na.rm=T))
# Remove outliers for map color scale
diff_rast[diff_rast < diff_range[1] | diff_rast > diff_range[2]] <- NA

h <- ggplot(data.frame(Difference=diff_vec, stringsAsFactors = FALSE), aes(Difference)) +
     geom_density(fill="grey") +
     ylab("Density") +
     xlab(expression(paste('% difference in primary production'))) +
     theme_bw() +
     theme(legend.position="none")

grid.arrange(spplot(stack(vgpm_rast, bio_rast), zlim=full_range),
             spplot(diff_rast, zlim=diff_range, main="% Difference"),
             ncol=2, widths=c(5,3))

suppressWarnings(print(h))

```
